Imm algorithm implementation for tracking

### 2020-01-31 Latex/exp.tex
Problems on measure
I think problems come from the nonlinearity of the measure model, gonna work on that, attempts with low R tend to yield better results (obviously)

    TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
    sensori circostanti))
    \\
    Sensors can communicate with the devices adjacent to them (Neighboorhood) and exchange with them signals named CanSense and CantSense
    which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.3\textwidth]{Immagini/Neighboors.png}
        \caption{Neighboors for a sensors are the one immediately adiacent. The purples ones represent the neighboors of green sensor}
        \label{fig:galaxy}
    \end{figure}
    \\
    % QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
    % \\
    % The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
    % more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
    % sensors as fully-connected, since the distance between them is short and they are directly linked.
    \\
    Different state can receive and send different messagesses. A sensor in On state has the moving
    object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
    Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
    if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
    A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
    can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
    \\
    When a sensor have the target in range it does a measure operation each timestep. the sensor works as a radar in this model and remembering
    \begin{equation}
        z(k)=h(x(k))+v(k)
    \end{equation}
    where $h(x)$ is the polar to cartesian cordinates transform and $v(k)$ is the noise associated to the measurement's operation.

>>>>

    TABELLA CON LE FUNZIONI DEGLI STATI (mettere di fianco al paragrafo sotto una immagine che fa  vederecosa intendiamo con neighboors (gli 8 
    sensori circostanti))
    \\
    Sensors can communicate with the devices adjacent to them (Neighboorhood) and exchange with them signals named CanSense and CantSense
    which state respectively whenever the agent gets in or goes out of the communicating sensor's range. This check is done through the 
    function inRange() that also serves as a switch between the states of the sensor, as already shown by the figure above.
    \begin{figure}[h!]
        \centering
        \includegraphics[width=0.3\textwidth]{Immagini/Neighboors.png}
        \caption{Neighboors for a sensors are the one immediately adiacent. The purples ones represent the neighboors of green sensor}
        \label{fig:galaxy}
    \end{figure}
    \\
    % QUESTO METTILO NEL CONSENSUS, NON HA SENSO PARLARNE QUI
    % \\
    % The set of active sensors inside the grid is dynamic, as vertices keep getting added and popped. However it has to be noticed, as stated before, that no 
    % more than 4 sensors will be ON at any point of time and they will all be adjacent to each other, this let us model the graph of the active 
    % sensors as fully-connected, since the distance between them is short and they are directly linked.
    \\
    Different state can receive and send different messagesses. A sensor in On state has the moving
    object in his range and send a CanSense to the nearby and when trackin moving away from the operating range send a CantSense turning itself to Idle.
    Sensors that receive a CanSense and are not already On turn in Idle state; during the Idle state sensors check
    if object appears in range sensors turn to On and send a CanSense, if nothing trigger the range it send to the nearby a CantSense signal.
    A sensor that is in Idle and during the information exchange receive only CantSense from the nearby turn itself Off and stop to check if somenthing is in range and
    can be turned again to Idle via a CanSense. This scheme implies that a sensors can never switch to On from Off except for the initialization step.
    \\
    Whenever the target is in range of a sensor, the device takes a measurement at each timestep.
    The model we choose for our measurement device is a radar and as such the measurement function 
    $z(k)=h(x(k))+v(k)$ associated with it is the cartesian to polar transformation, as shown below
    \begin{align*}
        &z(k)=h(x(k))+v(k)\\
        &\begin{bmatrix}
            \rho(k)\\ \alpha(k)
        \end{bmatrix}=  
        \begin{bmatrix}
            \sqrt{x(k)^2+y(k)^2}\\ atan2(y(k)/x(k))
        \end{bmatrix} +
        \begin{bmatrix}
            v_{1}(k)\\v_{2}(k)
        \end{bmatrix}
    \end{align*}
    where $h(x)$ is the polar to cartesian cordinates transform and $v(k)$ is the noise associated to the measurement's operation.
